\documentclass{muratcan_cv}

\setname{Aldo Ramón}{Franco Comas}
\setaddress{Madrid/Spain}
\setmobile{+34 639 606 821}
\setmail{aldo911012@gmail.com}
\setposition{Work Student} %ignored for now
\setlinkedinaccount{https://www.linkedin.com/in/aldofranco91} %you can play with color of the template (red is also nice..)
\setgithubaccount{https://github.com/aldofranco91} %you can play with color of the template (red is also nice..)
\setthemecolor{red} %you can play with color of the template (red is also nice..)

\begin{document}
%Set variables
%You can add sections, texts, explanations just by copying the style below. Replace the dummy texts "\lipsum[1][x-x]\par" with actual texts.
%Create header
\headerview
\vspace{1ex}
%Sections
%
% Summary
%\addblocktext{Summary}{%
%\lipsum[1][1-12]\ %replace this part with actual text
%}
%

% Experience
\section{Experience}
    %
    \datedexperience{\href{https://www.ncs-spain.com/ncssp/}{Network Centric Software, S.A, Madrid, Spain.}}{03/2020 - Today} 
    \explanation{External consultant in AXA Seguros S.A.}
    \explanationdetail{
     \coloredbullet\  Acquisition of data from open sources, applying statistical techniques, geospatial techniques and machine learning algorithms, in order to solve business and technical problems with impact on the company's priorities. \\
     \coloredbullet\  Work closely with the Data Engineers to design and implement the automation of processes and models in the production. \\
     \coloredbullet\  Contribute to extend the data culture of the company. \\
     \coloredbullet\  Technologies: R, Python, Scala, Spark and Azure. \\
     }
    %
    \datedexperience{\href{https://www.axa.es/}{AXA Seguros Generales S.A, Madrid, Spain.}}{09/2018 - 12/2019} 
    \explanation{Internship.} 
    \explanationdetail{
     \coloredbullet\  Acquisition of data from open sources, applying statistical techniques, geospatial techniques and machine learning algorithms, in order to solve business and technical problems with impact on the company's priorities. \\
     \coloredbullet\  Work closely with the Data Engineers to design and implement the automation of processes and models in the production. \\
     \coloredbullet\  Technologies: R and Python. \\
     }
  %
 \datedexperience{\href{https://www.uc3m.es/ss/Satellite/UC3MInstitucional/es/PortadaMiniSiteA/1371229065435/Departamento_de_Estadistica}{Universidad Carlos III de Madrid, Spain.}}{09/2017 - 09/2018} 
 \explanation{Teaching assistant.} 
 \explanationdetail{
 	\coloredbullet\ Department of Statistics. \\
 	\coloredbullet\ Tutorial classes of R and Matlab. \\
 }
    %
\datedexperience{\href{http://www.one.cu/}{National Office of Statistics and Information, Havana, Cuba.}}{09/2014 - 09/2016} 
\explanation{Statistician.} 
\explanationdetail{
	\coloredbullet\  Development and creation of national surveys. \\
	\coloredbullet\  Data cleaning, analytics, and visualization from the results obtained of these surveys. \\
	\coloredbullet\  Technologies: R, SPSS and Visual FoxPro. 
}
  

%Education
\section{Education} 
    \datedexperience
    {\href{https://www.uc3m.es/master/mathematical-engineering}{Universidad Carlos III de Madrid, Spain.}}{2017-2019} 
    \explanation{MSc. in Mathematical Engineering.} 
    % \explanationdetail{\coloredbullet\ % 
    % \lipsum[1][3-4]\par %replace this part with actual text
    % }
    \datedexperience
    {\href{https://www.escueladeempresa.com/cursos-universitarios-6-meses/curso-universitario-de-especializacion-en-introduccion-a-la-ciberseguridad/?ap=pago}{Escuela de Empresas, Madrid, Spain.}}{2019} 
    \explanation{Introduction to Cybersecurity.} 
%
    \datedexperience{\href{https://www.uc3m.es/master/big-data-analytics}{Universidad Carlos III de Madrid, Spain.}}{2016-2018} 
    \explanation{MSc. in Big Data and Analytics.} 
    \datedexperience{\href{http://www.uh.cu/matematica}{Universidad de La Habana, Cuba.}}{2010-2014}
    \explanation{BSc. in Mathematics.} 

    
%
% Skills
\section{Skills}
    %
    \newcommand{\skillone}{\createskill{Programming Languages}{\textbf{\emph{Experienced:}} \ \  Python \cpshalf R \ \ \textbf{\emph{Familiar:}} \ \  Scala \cpshalf Matlab \cpshalf Latex \cpshalf HTML }}
    %
    \newcommand{\skilltwo}{\createskill{Software Development}{GIT}}
    %
    \newcommand{\skillthree}{\createskill{Frameworks \ \& \ Libraries}{Jupyter \cpshalf Caret \cpshalf Numpy \cpshalf Pandas \cpshalf Scikit-learn \cpshalf Keras}}
    %
    \newcommand{\skillfour}{\createskill{Languages}{\textbf{\emph{Native:}} \ \  Spanish \ \ \textbf{\emph{Middle:}} \ \ English \ \ }}
    %
    \createskills{\skillone, \skilltwo, \skillthree, \skillfour}
%

\newpage
% Accomplishments
\section{Accomplishments}
 \datedexperience
 	{Third position in the  	\href{https://www.u-tad.com/alumnos-del-grado-ingenieria-software-u-tad-ganan-datathon-microsoft-espana/}{U-Tad Data Science Student Challenge.}}{2017}
 %\explanation{Master's Thesis Mathematical Engineering.} 
  \explanationdetail{
  	\coloredbullet\ First Microsoft datathon in Spain. \\
  	\coloredbullet\ Data analysis and pattern finding in a large, anonymized data base provided by the Santander Bank.     
  }
%

%Education
\section{Projects} 
\datedexperience
	{\href{https://github.com/aldofranco91/TFM_Ing_Mat/blob/master/!!Tesis/Aldo_TFM.pdf}{Nearest Neighbor Procedure with Partially Observed Distance Matrices.}}{2019} 
	\explanation{Master's Thesis Mathematical Engineering.}
	\explanationdetail{
		\coloredbullet\ Design a k-NN procedure when for reasons of response time, computational cost (e.g., in extremely large  	datasets) or destructive test it is not possible to calculate the distances between the new observations and all the observations in the training sample.
	} \\
%
\datedexperience
	{\href{https://github.com/aldofranco91/TFM_Big_Data/blob/master/!!Tesis/Aldo_TFM.pdf}{Forecasting Spanish electricity prices.}}{2018} 
	\explanation{Master's Thesis Big Data and Analytics.}
	\explanationdetail{
		\coloredbullet\ Forecast the electricity prices in short, medium and long. It was developed a website that allows to visualize and download these predictions and their corresponding prediction intervals.
	}

\section{Publications}
\datedexperience
{\href{https://www.funcas.es/wp-content/uploads/2021/06/An\%C3\%A1lisis-econom\%C3\%A9trico-y-big-data.pdf}{Econometric analysis and big data.}}{2021} \\
%
\datedexperience
{\href{https://1library.co/document/y4x1l85z-encuesta-indicadores-prevencion-infeccion-vih-sida.html}{Analysis of Indicators on HIV / AIDS infection in Cuba.}}{2015} 

%Footnote
%\createfootnote
\end{document}
